Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 12:14

author:
  - name:        Athanasios N. Natsis
    email:       natsisphysicist@gmail.com
    affiliation: LAP
    correspondingauthor: true
    # footnote: 1
  - name:        Alkiviadis Bais
    email:       abais@auth.gr
    affiliation: LAP
  - name:        Charikleia Meleti
    email:       meleti@auth.gr
    affiliation: LAP
    # footnote: 1
address:
  - code:         LAP
    organization: Laboratory of Atmospheric Physics, Physics Department, Aristotle University of Thessaloniki
    # addressline:  1 main street
    city:         Thessaloniki
    postcode:     54124
    country:      Greece
  # - code:         Another University
  #   organization: Department
  #   addressline:  A street 29
  #   postcode:     2054 NX
  #   city:         Manchester,
  #   state:        State
  #   country:      The Netherlands
# footnote:
#   - code: 1
#     text: "This is the first author footnote."
#   - code: 2
#     text: "Another author footnote."
abstract: |
  In this study, we investigate the characteristics of global horizontal
  irradiance enhancement events induced by clouds over Thessaloniki for
  the period 1994 -- 2023 using data recorded every one minute. To our
  knowledge, there isn't a similar study with such a long time series. We
  identified the cloud enhancement (CE) events by creating an appropriate
  cloud-free irradiance reference using a radiative transfer model and
  aerosol optical depth data from a collocated Cimel sun photometer and a
  Brewer spectrophotometer. We found a trend in CE events of
  \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
  The peak of the CE events was observed during May and June. CE events
  with duration longer than 10\nobreakspace{}min are very rare
  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
  minutes. Finally, we have detected enhancements above the total solar
  irradiance at the top of the atmosphere for the same solar zenith angle
  of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
  cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
  occur in spring -- early summer, with a secondary peak in autumn.

@@

biblio-style:   elsarticle-num-names # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme

@@

In this study, we investigate the characteristics of global horizontal irradiance
enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
using data recorded every one minute.  To our knowledge, there isn't a similar study
with such a long time series.  We identified the cloud enhancement (CE) events by
creating an appropriate cloud-free irradiance reference using a radiative transfer
model and aerosol optical depth data from a collocated Cimel sun photometer and a
Brewer spectrophotometer. We found a trend in CE events of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
`r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
and a trend in the corresponding irradiation of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
The peak of the CE events was observed during May and June. CE events with duration
longer than 10\nobreakspace{}min are very rare
($<`r ceiling(100*ST_G0[,sum(GLB_ench.N>10)/.N])`\,\%$), with exceptions lasting
over an hour and up to 140 minutes.  Finally, we have detected enhancements above the
total solar irradiance at the top of the atmosphere for the same solar zenith angle
of up to
$204\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
$40\,\text{W}/\text{m}^{2}$. Most of these extreme events occur in spring -- early
summer, with a secondary peak in autumn.
-->

>>>>

author:
  - name:        Athanasios N. Natsis
    email:       natsisphysicist@gmail.com
    affiliation: LAP
    correspondingauthor: true
    # footnote: 1
  - name:        Alkiviadis Bais
    email:       abais@auth.gr
    affiliation: LAP
  - name:        Charikleia Meleti
    email:       meleti@auth.gr
    affiliation: LAP
    # footnote: 1
address:
  - code:         LAP
    organization: Laboratory of Atmospheric Physics, Physics Department, Aristotle University of Thessaloniki
    # addressline:  1 main street
    city:         Thessaloniki
    postcode:     54124
    country:      Greece
  # - code:         Another University
  #   organization: Department
  #   addressline:  A street 29
  #   postcode:     2054 NX
  #   city:         Manchester,
  #   state:        State
  #   country:      The Netherlands
# footnote:
#   - code: 1
#     text: "This is the first author footnote."
#   - code: 2
#     text: "Another author footnote."
abstract: |
  In this study, we investigate the characteristics of global horizontal
  irradiance enhancement events induced by clouds over Thessaloniki for
  the period 1994 -- 2023 using data recorded every one minute. We
  identified the cloud enhancement (CE) events by creating an appropriate
  cloud-free irradiance reference using a radiative transfer model and
  aerosol optical depth data from a collocated Cimel sun photometer and a
  Brewer spectrophotometer. We found a trend in CE events of
  \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
  To our knowledge, such long-term changes in CE events have not been presented in the past.
  The peak of the CE events was observed during May and June. CE events
  with duration longer than 10\nobreakspace{}min are very rare
  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
  minutes. Finally, we have detected enhancements above the total solar
  irradiance at the top of the atmosphere for the same solar zenith angle
  of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of the
  cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme events
  occur in spring -- early summer, with a secondary peak in autumn.

@@

biblio-style:   elsarticle-harv # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
# biblio-style:   elsarticle-num-names # elsarticle-harv author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme

@@

In this study, we investigate the characteristics of global horizontal irradiance
enhancement events induced by clouds over Thessaloniki for the period 1994 -- 2023
using data recorded every one minute. We identified the cloud enhancement (CE) events by
creating an appropriate cloud-free irradiance reference using a radiative transfer
model and aerosol optical depth data from a collocated Cimel sun photometer and a
Brewer spectrophotometer. We found a trend in CE events of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.N",slope],0))`\pm
`r round(2*yearlyCE[var=="GLB_diff.N",slope.sd],0)`\,\text{cases}/\text{year}$,
and a trend in the corresponding irradiation of
$`r plus_sign(round(yearlyCE[var=="GLB_diff.sum",slope],1))`\pm
`r round(2*yearlyCE[var=="GLB_diff.sum",slope.sd],1)`\,\text{kJ}/\text{year}$.
To our knowledge, such long-term changes in CE events have not been presented in the past.
The peak of the CE events was observed during May and June. CE events with duration
longer than 10\nobreakspace{}min are very rare
($<`r ceiling(100*ST_G0[,sum(GLB_ench.N>10)/.N])`\,\%$), with exceptions lasting
over an hour and up to 140 minutes.  Finally, we have detected enhancements above the
total solar irradiance at the top of the atmosphere for the same solar zenith angle
of up to
$204\,\text{W}/\text{m}^{2}$, with the $75\,\%$ of the cases below
$40\,\text{W}/\text{m}^{2}$. Most of these extreme events occur in spring -- early
summer, with a secondary peak in autumn.
-->

### 2024-09-10 article/article.tex
Commit 2024-09-10 12:14

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}

@@

  \begin{abstract}
  In this study, we investigate the characteristics of global horizontal
  irradiance enhancement events induced by clouds over Thessaloniki for
  the period 1994 -- 2023 using data recorded every one minute. To our
  knowledge, there isn't a similar study with such a long time series.
  We identified the cloud enhancement (CE) events by creating an
  appropriate cloud-free irradiance reference using a radiative transfer
  model and aerosol optical depth data from a collocated Cimel sun
  photometer and a Brewer spectrophotometer. We found a trend in CE
  events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
  The peak of the CE events was observed during May and June. CE events
  with duration longer than 10\nobreakspace{}min are very rare
  (\(<8\,\%\)), with exceptions lasting over an hour and up to 140
  minutes. Finally, we have detected enhancements above the total solar
  irradiance at the top of the atmosphere for the same solar zenith
  angle of up to \(204\,\text{W}/\text{m}^{2}\), with the \(75\,\%\) of
  the cases below \(40\,\text{W}/\text{m}^{2}\). Most of these extreme
  events occur in spring -- early summer, with a secondary peak in
  autumn.
  \end{abstract}
    \begin{keyword}
    cloud enhancement \sep total solar radiation \sep global horizontal
irradiance \sep 
    over irradiance
  \end{keyword}

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}

@@

  \begin{abstract}
  In this study, we investigate the characteristics of global horizontal
  irradiance enhancement events induced by clouds over Thessaloniki for
  the period 1994 -- 2023 using data recorded every one minute. We
  identified the cloud enhancement (CE) events by creating an
  appropriate cloud-free irradiance reference using a radiative transfer
  model and aerosol optical depth data from a collocated Cimel sun
  photometer and a Brewer spectrophotometer. We found a trend in CE
  events of \(+112\pm 35\,\text{cases}/\text{year}\), and a trend in the
  corresponding irradiation of \(+329.9\pm 112\,\text{kJ}/\text{year}\).
  To our knowledge, such long-term changes in CE events have not been
  presented in the past. The peak of the CE events was observed during
  May and June. CE events with duration longer than 10\nobreakspace{}min
  are very rare (\(<8\,\%\)), with exceptions lasting over an hour and
  up to 140 minutes. Finally, we have detected enhancements above the
  total solar irradiance at the top of the atmosphere for the same solar
  zenith angle of up to \(204\,\text{W}/\text{m}^{2}\), with the
  \(75\,\%\) of the cases below \(40\,\text{W}/\text{m}^{2}\). Most of
  these extreme events occur in spring -- early summer, with a secondary
  peak in autumn.
  \end{abstract}
    \begin{keyword}
    cloud enhancement \sep total solar radiation \sep global horizontal
irradiance \sep 
    over irradiance
  \end{keyword}
